\documentclass[]{article}
\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[utf8]{inputenc}
\else % if luatex or xelatex
  \ifxetex
    \usepackage{mathspec}
    \usepackage{xltxtra,xunicode}
  \else
    \usepackage{fontspec}
  \fi
  \defaultfontfeatures{Mapping=tex-text,Scale=MatchLowercase}
  \newcommand{\euro}{€}
\fi
% use microtype if available
\IfFileExists{microtype.sty}{\usepackage{microtype}}{}
\ifxetex
  \usepackage[setpagesize=false, % page size defined by xetex
              unicode=false, % unicode breaks when used with xetex
              xetex]{hyperref}
\else
  \usepackage[unicode=true]{hyperref}
\fi
\hypersetup{breaklinks=true,
            bookmarks=true,
            pdfauthor={},
            pdftitle={},
            colorlinks=true,
            citecolor=blue,
            urlcolor=blue,
            linkcolor=magenta,
            pdfborder={0 0 0}}
\urlstyle{same}  % don't use monospace font for urls
\setlength{\parindent}{0pt}
\setlength{\parskip}{6pt plus 2pt minus 1pt}
\setlength{\emergencystretch}{3em}  % prevent overfull lines
\setcounter{secnumdepth}{0}

\author{}
\date{}

\begin{document}

\section{Graph Theory Facts and
Propositions}\label{graph-theory-facts-and-propositions}

\subsection{General:}\label{general}

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\itemsep1pt\parskip0pt\parsep0pt
\item
  Handshake Theorem: $\sum_{v \in V(G)} deg(v) = 2|E|$
\item
  Proposition: Every graph with $\geq 2$ vertices has \textbf{two
  vertices} of the \textbf{same degree.}
\item
  Proposition: the n-cube has $2^n$ vertices and $n2^{n-1}$ edges
\item
  Theorem: if there is a walk from vertex x to vertex y in G then there
  is a path from x to y in G.
\item
  Corollary: if there is a path from x to y in G and a path from y to z
  in G then there is a path from x to z in G.
\item
  Theorem: let G be a graph and let v be a vertex in G. If for each w in
  G there is a path from v to w, then G is connected. \emph{For any
  vertex, you can get to any other vertex.}
\item
  Theorem: a graph G is \textbf{not connected} iff there exists a proper
  subset of x of V(G) such that the \textbf{cut} induced by x is empty.
\item
  Proposition: if every very has degree $\geq 2$ then G \textbf{has a
  cycle}.
\item
  Theorem (Dirac): if G is a graph on \textbf{n $\geq$ 3 vertices} where
  every vertex has degree $\geq \frac{n}{2}$, then G has a cycle
  containing every vertex. G is a \textbf{Hamiltonian Graph}.
\item
  Theorem (Chvtal '72): if G is a graph on n vertices with degree
  $d_1 \leq d_2 \leq d_3 ... \leq d_n$ then if $d_i \geq i$ or
  $d_{n-i} \geq n - i$ for all $i \leq \frac{n}{2}$, then G is
  Hamiltonian.
\item
  Theorem (Tutte): Every \textbf{4-connected} planar graph is
  \textbf{Hamiltonian}.
\item
  Theorem: Every connected graph in which every vertex has even degree
  is \emph{Eulerian}. An Eulerian graph has an Euler tour, which is a
  closed walk that contains every edge once.
\item
  Lemma: if e = \{x,y\} is a bridge of a connected graph G, then G-e has
  precisely two components. Furthermore, x and y are in different
  components.
\item
  Theorem: An edge is a bridge of a graph G iff it is \textbf{not
  contained in a cycle of G}.
\item
  Corollary: If there are two distinct paths from u to v in G then G
  contains a cycle.
\item
  Lemma: There is a unique path between every pair of vertices u and v
  in a tree.
\item
  Lemma: \textbf{Every edge} of a tree T is a \textbf{bridge}.
\item
  Theorem: A tree with \textbf{at least 2 vertices} has at least two
  vertices of \textbf{degree 1}.
\item
  Theorem: if T is a tree, then \textbar{}E(T)\textbar{} =
  \textbar{}V(T) - 1\textbar{}.
\item
  Proposition: If x,y are vertices of a tree T, then there is a unique
  path of T from x to y.
\item
  Proposition: A graph G has a \textbf{spanning tree} iff it is
  \textbf{connected}.
\item
  Corollary: Every connected graph on n vertices has $\geq n-1$ edges.
\item
  Corollary: Every \textbf{connected} graph on n vertices, n-1 edges
  \textbf{is a tree}.
\item
  Proposition: Every tree is \textbf{bipartite}.
\item
  Proposition: If G is a bipartite graph and u,v $\in V(G)$ then if u
  and v are in the \textbf{same part} of a bipartition, then every walk
  from u to v has \textbf{even length}. If u,v are in \textbf{different
  parts}, then every walk from u to v has \textbf{odd length}.
\item
  Proposition: If G is a graph with no \textbf{odd cycles}, then
  \textbf{G is bipartite}.
\item
  Theorem: Prim's algorithm outputs a min-weight spanning tree.
\item
  Proposition: A graph is planar iff it has a spherical embedding.
\item
  Theorem: If a connected planar embedding has faces $f_1, f_2, ...$
  then $\sum_{i=1} deg(f_i) = 2|E(G)|$
\item
  Corollary: If the connected graph G has a planar embedding with f
  faces, then average degree of a face is $\frac{2|E(G)|}{f}$.
\item
  Theorem (Euler): let G be a connected graph with \textbar{}V\textbar{}
  vertices and \textbar{}E\textbar{} edges. If G has a planar embedding
  with \textbar{}F\textbar{} faces, then \textbar{}V\textbar{} -
  \textbar{}E\textbar{} + \textbar{}F\textbar{} = 2.
\item
  Theorem: There are exactly \textbf{five} \emph{non-isomorphic, planar
  dual, platonic solids}:

  \begin{enumerate}
  \def\labelenumii{\arabic{enumii}.}
  \itemsep1pt\parskip0pt\parsep0pt
  \item
    Tetrahedron:

    \begin{enumerate}
    \def\labelenumiii{\arabic{enumiii}.}
    \itemsep1pt\parskip0pt\parsep0pt
    \item
      4 faces
    \item
      4 vertices
    \item
      6 edges
    \end{enumerate}
  \item
    Cube:

    \begin{enumerate}
    \def\labelenumiii{\arabic{enumiii}.}
    \itemsep1pt\parskip0pt\parsep0pt
    \item
      6 faces
    \item
      8 vertices
    \item
      12 edges
    \end{enumerate}
  \item
    Octahedron:

    \begin{enumerate}
    \def\labelenumiii{\arabic{enumiii}.}
    \itemsep1pt\parskip0pt\parsep0pt
    \item
      8 faces
    \item
      6 vertices
    \item
      12 edges
    \end{enumerate}
  \item
    Icosahedron:

    \begin{enumerate}
    \def\labelenumiii{\arabic{enumiii}.}
    \itemsep1pt\parskip0pt\parsep0pt
    \item
      20 faces
    \item
      12 vertices
    \item
      30 edges
    \end{enumerate}
  \item
    Do-decahedron:

    \begin{enumerate}
    \def\labelenumiii{\arabic{enumiii}.}
    \itemsep1pt\parskip0pt\parsep0pt
    \item
      12 faces
    \item
      20 vertices
    \item
      30 edges
    \end{enumerate}
  \end{enumerate}
\item
  Lemma: Let G be a planar embedding with \textbar{}V\textbar{}
  vertices, \textbar{}E\textbar{} edges and \textbar{}F\textbar{} faces.
  Then \{d,k\} is one of the five pairs of faces and vertices: \{3,3\},
  \{3,4\}, \{4,3\}, \{5,3\}, \{3,5\}
\item
  Lemma: If G is \textbf{connected} and \textbf{not a tree} then in a
  planar embedding of G, the boundary of each face contains a
  \textbf{cycle}.
\item
  Lemma: Let G be a planar embedding with \textbar{}V\textbar{} vertices
  and \textbar{}E\textbar{} edges. If each face has degree at least d,
  then (d-2)\textbar{}E\textbar{} $\leq$ d(\textbar{}V\textbar{}-2)\$.
\item
  Corollary: In any planar embedding of a graph with \textbf{at least 2
  edges}, \textbf{each face} has degree $\geq 3$.
\item
  Lemma: In any planar embedding of a graph with $\geq$ \textbf{1
  cycle}, the \textbf{boundary} of every face \textbf{contains a cycle}.
\item
  Lemma (Test 1): If G = (V,E) is a planar graph and
  \textbar{}E\textbar{} $\geq 2$, then \textbar{}E\textbar{} $\leq$
  3\textbar{}V\textbar{}-6.
\item
  Corollary: $K_5$ is non-planar \textbar{}V\textbar{} = 5,
  \textbar{}E\textbar{} = 10.
\item
  Corollary: A \textbf{planar graph} has a \emph{vertex of degree at
  most 5}.
\item
  Lemma (Test 2): If G = (V,E) is a planar graph and every cycle has
  length $\geq$ g, where g is the \textbf{girth}, the length of the
  smallest cycle, and \textbar{}E\textbar{} $\geq \frac{1}{2}g$, then
  $|E| \leq \frac{g}{g-2}(|V| - 2)$
\item
  Corollary: $K_{3,3}$ is non-planar because it has no triangles, so g =
  4 and it fails Test 2.
\item
  Kuratowski's Theorem: A graph is planar \textbf{iff} it has \textbf{no
  subdivision} of $K_{3,3}$ or $K_5$ as a \textbf{subgraph}.
\item
  Theorem: A graph is \textbf{2-colourable} iff it is
  \textbf{bipartite}.
\item
  Theorem: $K_n$ is n-colourable and not k-colourable for k \textless{}
  n.
\item
  Five-Colour-Theorem: \textbf{Every} planar graph is
  \textbf{5-colourable}.
\item
  Theorem: \textbf{Every} planar graph is \textbf{4-colourable}.
\item
  Lemma: M is \textbf{not} a \textbf{maximum matching} iff there exists
  an \textbf{M-augmenting path}.
\item
  Lemma: If M is a \textbf{matching} of G and C is a \textbf{cover} of G
  then $|M| \leq |C|$.
\item
  Lemma: If M is matching and C is a cover and \textbar{}M\textbar{} =
  \textbar{}C\textbar{} then M is a maximum matching and C is a minimum
  cover.
\item
  Theorem (Konig's Theorem): If G is \textbf{bipartite}, then the size
  of the \textbf{maximum matching} is \textbf{equal} to the size of the
  \textbf{minimum cover}.
\item
  Lemma: Let G be a \textbf{bipartite} graph with bipartition A,B where
  \textbar{}A\textbar{} = \textbar{}B\textbar{} = n. If G has
  \textbar{}E\textbar{} edges then \textbf{G has a matching} of
  \textbf{at least} size $\frac{|E|}{n}$.
\item
  Theorem (Hall's): An (A,B)-bigraph G has a matching that
  \textbf{saturates} A iff for \textbf{every subset} S of A,
  \textbar{}S\textbar{} $\leq$ \textbar{}N(S)\textbar{}.
\item
  Corollary: An (A,B) bigraph G has a \textbf{perfect matching} iff
  \textbar{}A\textbar{}=\textbar{}B\textbar{} and for S is a subset of
  A, \textbar{}S\textbar{} $\leq$ \textbar{}N(S)\textbar{}.
\item
  Proposition: If k $\geq 1$ and G is a \textbf{k-regular, bipartite}
  graph, then G has a \textbf{perfect matching}.
\item
  Corollary: If G is a \textbf{k-regular, bipartite} graph, then E(G)
  has a partition into \textbf{k perfect matches} of G.
\item
  Corollary: Following from right above, \textbf{every k-regular,
  bipartite} graph is \textbf{k-edge colourable}.
\end{enumerate}

\end{document}
